Holomorphic field theories and higher algebra

### 2024-10-12 draft.tex

\owen{Draw some 2d pictures and unpack a little. Mention pair of pants \& OPE} 
In this sense, it captures the dependence on the discs.

>>>>

To illustrate the idea, we take $d=2$ and draw a point in the configuration space~$\Disc_2(2)$:
\begin{center}
  \begin{tikzpicture}
   \draw[semithick] (0,0) circle (2.5);
   \draw[semithick] (0,0) circle (0.75);
   \draw[semithick] (1,1) circle (0.5);
   \fill (0,0) circle (0.05) node [below right] {$0$};
   \fill (1,1) circle (0.05) node [below right] {$p$};
\end{tikzpicture}
\end{center}
where there is a disc centered at the origin with larger radius and a disc centered at a point~$p$ with smaller radius.
This picture clearly resembles the ``pair of pants" product from two-dimensional topological field theories, but pressed flat.
To a physicist, this picture encodes a way of multiplying an operator with support near 0 by an operator with support near $p$ to get an operator with support near the origin (although the support is larger);
they use the term {\em operator product expansion} when they express this multiplication in formulas.
